The coverage fraction of starspots on young Taurus members and consequences for stellar ages estimates at 1$-$10 Myr

### 2018-09-18 document/ms.tex
Add prose about measurement philosophy and spectral method.  tick off some outline tasks.

Deriving amplitudes from sinusoidal lightcurves should be as simple as measuring the peak-minus-valley flux differences.  In practice, additional factors complicate such a straightforward analysis.  One main uncertainty is how to treat \emph{secular} trends, in which the star's flux waxes and wanes with both an oscillatory function of periods $P_{\rm rot}$ and with a slow-varying mean level with characteristic timescales $t_{\rm secular}$.  Secular changes in flux could be interpreted as a growing or waning average starspot coverage fraction as in a long-term stellar activity cycles.  The interpretation of secular trends depends on to-what-extent instrumental artifacts mimic these time-series structures.  In Kepler/K2, for example, spurious secular trends can exist at the few percent level as point spread functions leak out of pre-defined aperture masks due to spacecraft-induced image motion, thermal effects, and other instrumental systematic effects.  Increasing aperture size can sometimes, partially mitigate these biases at the expense of greater variance and read noise.  The characteristic timescales of these instrumental biases tend to resemble the observing season- either campaigns for K2, or quarters for Kepler prime.  Disk-free young stars exhibit bona fide secular trends of up to half a magnitude over periods of years-decades based on decades of ground-based photometric monitoring \citep{grankin08}.

@@

@@

We derived starspot temperatures and areal filling factors from IGRINS $H-$band spectra using the inference framework \texttt{Starfish} \citep{czekala15}, as extended by \citet{2017ApJ...836..200G}.  We employed PHOENIX synthetic model with an updated version of \texttt{Starfish} that maintains the native absolute fluxes from \citet{husser13}, rather than the slightly inaccurate interpolation introduced in the Appendix of \citet{2017ApJ...836..200G}.  We ran 5000 samples with 40 \texttt{emcee} walkers \citep{foreman13}, with manual spot-checking of convergence.  We find typical filling factors around $f_\mathrm{spot} \sim 75\%$ and temperatures $T_\mathrm{spot} \sim 2600$ K.

>>>>

Deriving amplitudes from sinusoidal lightcurves should be as simple as measuring the peak-minus-valley flux differences.  In practice, additional factors complicate such a straightforward analysis.  One main uncertainty is how to treat \emph{secular} trends, in which the star's flux waxes and wanes with both an oscillatory function of periods $P_{\rm rot}$ and a slow-varying mean level with characteristic timescale $t_{\rm secular}$.  Secular changes in flux could be interpreted as a growing or waning average starspot coverage fraction as in a long-term stellar activity cycle.  The interpretation of secular trends depends on to-what-extent instrumental artifacts mimic these time-series structures.  In Kepler/K2, for example, spurious secular trends can exist at the few percent level as point spread functions leak out of pre-defined aperture masks due to spacecraft-induced image motion, thermal effects, and other instrumental systematic effects.  Increasing aperture size can sometimes, partially mitigate these biases at the expense of greater variance and read noise.  The characteristic timescales of these instrumental biases tend to resemble the observing season- either campaigns for K2, or quarters for Kepler prime.  Meanwhile, disk-free young stars exhibit bona fide secular trends of up to half a magnitude over periods of years-decades based on decades of ground-based photometric monitoring \citep{grankin08}.

@@

\subsection{Two-temperature spectral inference framework}

We employ the \texttt{Starfish}\footnote{Forked from the original (\href{https://github.com/iancze/Starfish}) at https://github.com/gully/Starfish} \citep{czekala15} spectral inference framework, as adapted from  by \citet{2017ApJ...836..200G}.  The \texttt{Starfish} framework builds a forward-model of the observed spectrum based spectrally emulated pre-computed synthetic model grid spectra.  We employed the PHOENIX synthetic model with an updated version of \texttt{Starfish} that maintains the native absolute fluxes from \citet{husser13}, rather than the inaccurate interpolation introduced in the Appendix of \citet{2017ApJ...836..200G}.

The likelihood-based Bayesian inference framework \texttt{Starfish} is for evaluating the posterior probability of parameters given an observed spectrum, \emph{assuming the model is correct}.  The model assumptions are:

\begin{itemize}
  \item Stellar photospheres are composed of exactly two distinct temperature components.
  \item Most of the spectral lines arise from known stellar atmospheric physics \citep{husser13}.
  \item The low temperature is above some finite threshold, typically $T>2400$ K.
  \item The two components share the same surface gravity and metallicity.
\end{itemize}

The inference framework provides a \emph{measurement} of the temperatures and projected filling factor of the two components.  The inference framework makes no effort to conduct \emph{model comparison}--- whether two temperature components are really needed over one, for example, or whether-or-not three components are warranted to capture additional, unexplained variance.  Nor does the framework conduct \emph{detection} of starspots-- detection has usually already been established by the high precision photometric time series observations that reveal conspicuous undulations indicative of distinct surface structures with distinct emergent photospheres.  We know the spots are there.  We simply aim to quantify the first moment of their physical properties-- the average coverage fractions, and the characteristic temperatures.

@@

We derived starspot temperatures and areal filling factors from IGRINS $H-$band spectra using the inference framework \texttt{Starfish} \citep{czekala15}, as extended by \citet{2017ApJ...836..200G}.  We ran 5000 samples with 40 \texttt{emcee} walkers \citep{foreman13}, with manual spot-checking of convergence.  We find typical filling factors around $f_\mathrm{spot} \sim 75\%$ and temperatures $T_\mathrm{spot} \sim 2600$ K.
